|

### 2021-02-24 manuscript/article.Rmd
small updates

---
title:  |
        | Financial Incentives and Healthcare Provision: Evidence from an Experimental *Aedes aegypti* Control Programme in Brazil
author:
  - Danilo Freire[^freire]
  - Umberto Mignozzetti[^mignozzetti]
date: \today
thanks: "We thank Saad Gulzar, Cathy Hafer, Dimitri Landa, Rebecca Morton, Adam Przeworski, Catarina Roman, Renard Sexton, David Skarbek, Denis Stukal, and participants at EGAP, MPSA, NYU PE Seminar, and SPSA for their valuable comments. We also thank the FGV Applied Research Centre for funding this research. Each named author has equally contributed to conducting the underlying research and drafting this manuscript. To the best of our knowledge, the authors have no conflict of interest, financial or otherwise. Replication materials are available at <http://github.com/danilofreire/incentives-healthcare>."
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: unsrtnat
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: template.latex
---

```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=T}
# If you need to install any package while knitting the document
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)

@@

The *Aedes aegypti* mosquito is the major worldwide vector of several arboviral
diseases, including chikungunya, dengue, yellow fever, and Zika
[@burt2012chikungunya; @jansen2010dengue; @leta2018global;
@thangamani2016vertical]. Over the last decades, arboviral incidence has
increased exponentially, with estimates suggesting that dengue is endemic in
over 100 countries and causes 400 million infections and 22 thousand deaths
each year [@bhatt2013global; @cdc2020dengue]. Since there are no safe vaccines
for most *Aedes*-transmitted diseases [@world2017dengue], we have seen a number
of dengue and Zika outbreaks in Asia, the Caribbean, South America, and the
United States [@carlson2016ecological; @leta2018global]. Chikungunya virus,
previously endemic only to Africa, has already been reported in every region of
the world [@grandadam2011chikungunya; @kraemer2015global; @mayer2017emergence].

>>>>

---
title:  |
        | Financial Incentives and Healthcare Provision: Evidence from an Experimental *Aedes aegypti* Control Programme in Brazil
author:
  - Danilo Freire[^freire]
  - Umberto Mignozzetti[^mignozzetti]
date: \today
thanks: "We thank Taylor Boas, Saad Gulzar, Cathy Hafer, Daniel Hidalgo, Dimitri Landa, Rebecca Morton, Adam Przeworski, Catarina Roman, Renard Sexton, David Skarbek, Denis Stukal, and participants at EGAP, MPSA, NYU PE Seminar, and SPSA for their valuable comments. We also thank the FGV Applied Research Centre for funding this research. Each named author has equally contributed to conducting the underlying research and drafting this manuscript. To the best of our knowledge, the authors have no conflict of interest, financial or otherwise. Replication materials are available at <http://github.com/danilofreire/incentives-healthcare>."
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: unsrtnat
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: template.latex
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# If you need to install any package while knitting the document
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)

@@

The *Aedes aegypti* mosquito is the major worldwide vector of several arboviral
diseases, including chikungunya, dengue, yellow fever, and Zika
[@boas2019electoral; @burt2012chikungunya; @jansen2010dengue; @leta2018global;
@thangamani2016vertical]. Over the last decades, arboviral incidence has
increased exponentially, with estimates suggesting that dengue is endemic in
over 100 countries and causes 400 million infections and 22 thousand deaths
each year [@bhatt2013global; @cdc2020dengue]. Since there are no safe vaccines
for most *Aedes*-transmitted diseases [@world2017dengue], we have seen a number
of dengue and Zika outbreaks in Asia, the Caribbean, South America, and the
United States [@carlson2016ecological; @leta2018global]. Chikungunya virus,
previously endemic only to Africa, has already been reported in every region of
the world [@grandadam2011chikungunya; @kraemer2015global; @mayer2017emergence].
